---
title: "Untitled"
author: "Lohannes"
date: "8/8/2019"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Wrangling

## Install Library

```{r}
library(dplyr)
library(GGally)
library(car)
library(lmtest)
library(tidyverse)
```

## Read Dataset 'World-Happiness-Report-2019'

```{r}
hw <- read.csv("world-happiness-report-2019.csv")
head(hw)
```

## Cleaning Dataset and Drop NA

```{r}
hw2 <- lapply(hw[,-c(1,2)],as.numeric) %>% 
  as.data.frame()
hw2 <- drop_na(hw2)
colSums(is.na(hw2))
```

## Modeling and Look Outlier

```{r}
modelhw1 <- lm(Positive.affect ~., hw2)
summary(modelhw1)
plot(modelhw1)
```

## Look for Formula

```{r}
step(modelhw1, direction = "backward")
```

## Summarize Formula

```{r}
hw_reg <- lm(formula = Positive.affect ~ SD.of.Ladder + Negative.affect + 
    Social.support + Freedom + Generosity, data = hw2)

summary(hw_reg)
```

Remove the `Negative.affect` and` Generosity` predictors which are insignificant predictors, and get the results:

```{r}
hw_new <- lm(formula = Positive.affect ~ SD.of.Ladder + Social.support + Freedom, data = hw2)

summary(hw_new)
```

### Linearity & Multicollinearity Test

```{r}
cor.test(hw2$Social.support, hw2$Positive.affect)
cor.test(hw2$Generosity, hw2$Positive.affect)
cor.test(hw2$Freedom, hw2$Positive.affect)
cor.test(hw2$Negative.affect, hw2$Positive.affect)
cor.test(hw2$Generosity, hw2$Positive.affect)
```

```{r}
hw_reg1 <-  hw2[, c('Positive.affect',"Negative.affect",'SD.of.Ladder', 'Social.support', 'Freedom',"Generosity")]
ggcorr(hw_reg1, label = T,label_size = 3)
```

```{r}
hw_new1 <-  hw2[, c('Positive.affect','SD.of.Ladder', 'Social.support', 'Freedom')]
ggcorr(hw_new1, label = T,label_size = 3)
```

## Normality Test

```{r}
vif(hw_reg)
shapiro.test(hw_reg$residuals)
bptest(hw_reg)
```

```{r}
vif(hw_new)
shapiro.test(hw_new$residuals)
bptest(hw_new)
```

# Explanation

## 1. From the process of finding a model to calculate the level of community happiness in each country, in terms of the 'Positive.affect' level which is calculated with various available predictors, including getting results:

a. Primary Variable:
- `Positive.affect` is influenced by` SD.of.Ladder` or the level of life that can be achieved by each community in a different country, where the small number of `SD.of.Ladder` also understands the number of` Positive.affect`
- 'Positive.affect' is influenced by `Freedom 'or the level of freedom given by the government to its people, where a large number of' Freedom 'will affect an even greater' Positive.affect 'number
- `Positive.affect` is influenced by` Social.support` or the level of social support provided by the government to its people, where the small number of `Social.support` also understands the value of` Positive.affect`

b. Supporting variables:
- `Positive.affect` is influenced by` Negative.affect` or negative emotions that exist in the community, where the variables `Positive.affect` and` Negative.affect` have inversely proportional properties, where if `Positive.affect` increases then` Negative ' .affect` goes down, and vice versa
- `Positive.affect` is influenced by` Generosity` or the level of generosity that exists in the community, where a large number of `Generosity` will affect an even greater 'Positive.affect` number


## 2. Carry out a feasibility test on the model that has been made, and compare the results of the feasibility test between model 1 (the basic model) and model 2 (the simplified model), the test is conducted using the Linearity, Multicolinearity, Heteroscedasticity, Normality, and obtaining methods results as follows:

model 1: basic model (Positive.affect ~ SD.of.Ladder + Negative.affect + Social.support + Freedom + Generosity)

- Multiple R-squared: 0.5472, Adjusted R-squared: 0.5303
- SD.of.Ladder, Freedom, Social.support was noted as a significant variable. Negative.affect & Generosity are recorded as significant variables
- cor test: Social.support p-value = 8.901e-08, Generosity p-value = 2.959e-07
Freedom p-value <2.2e-16, Negative.affect p-value = 2.011e-05, Generosity p-value = 2.959e-07, all five variables get p-values below 0.05, indicating that they are recorded as significant variables
- Normality test: SD.of.Ladder - 1.947020, Negative.affect - 2.222780 Social.support - 2.276327, Freedom - 1.570870, Generosity - 1.502879 (passed the test)
- Shapiro test: p-value = 0.532 (passed the test)
- BP test: p-value = 0.7028 (passed the test)

model 2: simplified model (Positive.affect ~ SD.of.Ladder + Social.support + Freedom)

- Multiple R-squared: 0.5317, Adjusted R-squared: 0.5214
- SD.of.Ladder, Freedom, Social.support was noted as a significant variable.
- cor test: Social.support p-value = 8.901e-08, Generosity p-value = 2.959e-07
Freedom p-value <2.2e-16, all three variables get p-values below 0.05, indicating that they are recorded as significant variables
- Normality test: SD.of.Ladder - 1.567095, Social.support - 1.905438, Freedom - 1.300738 (passed the test)
- Shapiro test: p-value = 0.3751 (passed the test)
- BP test: p-value = 0.7644 (passed the test)


## 3. provide recommendations on models that have been made

- after testing the feasibility of model 1 (Positive.affect ~ SD.of.Ladder + Negative.affect + Social.support + Freedom + Generosity) and model 2 (Positive.affect ~ SD.of.Ladder + Social.support + Freedom ), it can be concluded using model 2 will be more efficient and effective because the predictors used are simpler or simpler and will make it easier to do modeling.

- the model obtained can also be carried out with a better feasibility test if there is more data collected.
